Synthesis of Rules for Network Intrusion Detection

### 2019-10-19 paper/paper.tex
pass on abstract

\begin{document}
%
\title{Synthesis of Network Intrusion Detection Rules}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Lucas Alcantara\inst{1}\Comment{\orcidID{0000-1111-2222-3333}} \and
Guilherme Padilha\inst{1}\Comment{\orcidID{1111-2222-3333-4444}} \and
Marcelo d'Amorim\inst{1}\Comment{\orcidID{0000-0002-1323-8769}}}
%
\authorrunning{Alcantara et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Federal University of Pernambuco (UFPE), Recife, Brazil\\
\email{\{lama,ghps,damorim\}@cin.ufpe.br}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
...
\keywords{NIDS, synthesis, search}
\end{abstract}
%
%
%
\section{Introduction}

>>>>

\begin{document}
%
\title{Synthesis of Rules for Network Intrusion Detection}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Lucas Alcantara\inst{1}\Comment{\orcidID{0000-1111-2222-3333}} \and
Guilherme Padilha\inst{1}\Comment{\orcidID{1111-2222-3333-4444}} \and
Marcelo d'Amorim\inst{1}\Comment{\orcidID{0000-0002-1323-8769}}}
%
\authorrunning{Alcantara et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Federal University of Pernambuco (UFPE), Recife, Brazil\\
\email{\{lama,ghps,damorim\}@cin.ufpe.br}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Network Intrusion Detection Systems (\nids{}) are a popular defense
mechanism against network attacks today. These systems monitor the
network traffic and flag suspicious network behavior. Signature-based
\nids\ do that by checking the network traffic against a pre-defined
set of rules, which can become obsolete due to the adaptation of
attackers to existing rules. This paper proposes \tname{}, a technique
to synthesize rules for \nids; \tname{} uses previously-classified
positive and negative examples (\ie{}, malicious and benign traffic)
to identify the constraints that distiguish positive and negative
examples. In a nutshell, \tname{} bootstraps the search with a
candidate solution that uses data from the payload of the malicious
message, optimizes the candidate solution to capture the positive
example and, and then optimizes the candidate solution to avoid
capturing the negative traffic. Results indicate that \Fix{...}

\keywords{NIDS, synthesis, search}
\end{abstract}
%
%
%
\section{Introduction}
